A Case Study in Preserving a High Energy Physics Application

### 2014-02-24 paper.tex
experiment data rearrangement

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & hdfs & 33TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 1.16TB & 449MB & 5.2MB\\ \hline
        Tau source       & git & 51MB & 51MB & 51MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & hpc fs & 206TB & ??? & 119MB \\ \hline
        Linux commands & local fs & ??? & ??? & 88.4MB \\ \hline     
        Total          &          & ??? & ??? & ??? \\ \hline
    \end{tabular}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

\begin{figure}
\centering
\epsfig{file=package-info.eps, height=1.5in, width=2.5in}
\caption{Package Description Infomation}
\label{fig:package-info}
\end{figure}
The command used to generate the package containing all the files of L1 is as follows. 
`package1-4.sh` is a bash script which iterates each line of L1 and
determines the behavior according to the file type (common files, directories,
linked files) and the system call type.
The package description information is shown in Figure~\ref{fig:package-info}.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    Path used in Program & Actual Location \\ \hline
    / & /tmp/package1-4 \\ \hline
    /tmp/package1-4 & /tmp/package1-4 \\ \hline
    /dev & /dev \\ \hline
    /misc & /misc\\ \hline
    /net & /net\\ \hline
    /proc & /proc\\ \hline
    /sys & /sys\\ \hline
    /var & /var\\ \hline
    /selinux & /selinux\\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

@@

\begin{table*}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
        Solution 1& grid & CMSSW Git HTTP & email \\ \hline
        Solution 2& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        Solution 4& package & package & shell script + packaging utility \\ \hline
    \end{tabular}
    \caption{The relationship of different solutions}
    \label{table:relationship}
\end{table*}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Sub-Task & Time & Percentage \\ \hline
    Software acquisition from CMSSW & 15min 30s & 25.27\% \\ \hline
    Software acquisition from Git & 9s & 0.24\% \\ \hline
    Software acquisition from Wget & 36s & 0.98\% \\ \hline
    Environment Build - SCRAM & 13min 20s & 21.74\% \\ \hline
    Environment Build - Python & 1s & 0.03\% \\ \hline
    Data analysis & 31min 44s & 51.74\% \\ \hline
    Total & 61min 20s & 100.00\% \\ \hline
    \end{tabular}
    \caption{Breakdown of Execution Time of Solution 2}
    \label{table:time-2nd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Data Category & Data Size \\ \hline
    Software from CMSSW & 449MB \\ \hline
    Software from Git & 61MB \\ \hline
    Software from Wget & 52MB \\ \hline
    Hadoop & 33TB \\ \hline
    Total & 33792.562GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 2}
    \label{table:datasize-2nd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Sub-Task & Time \\ \hline
    Obtain file namelist & 37min 51s \\ \hline
    Generate P1 & 13min 37s \\ \hline
    Re-run the program within P1 & 13min 5s \\ \hline
    \end{tabular}
    \caption{Time Breakdown of Solution 4}
    \label{table:time-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Data Category & Data Size \\ \hline
    Hadoop & 20GB \\ \hline
    CMSSW\_5\_3\_11\_patch3 & 5.2MB \\ \hline
    pscratch & 119MB \\ \hline
    usr & 60MB \\ \hline
    Others (/sbin + ... + /lib) & 28.4MB \\ \hline
    Total & 20.213GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 4}
    \label{table:datasize-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
     Data Category & Data Size & Data Size \\
    & Solution 2 & Solution 4\\ \hline
    Hadoop & 33TB = 33792GB & 20GB \\ \hline
     CMSSW\_5\_3\_11\_patch3 & 562MB & 5.2MB \\ \hline
     Other data for Package & 207.4MB & N/A \\ \hline
     Total & 33792.562GB & 20.213GB \\ \hline
    \end{tabular}
    \caption{Data Size Comparison beweeen Solution 2 and 4}
    \label{table:datasize-2nd3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Task Category & Execution Time & Execution Time \\
    & Solution 2 & Solution 4\\ \hline
    Software Acquisition & 16min 15s & N/A \\ \hline
    Environment Building & 13min 21s  & 4s \\ \hline
    Obtain file namelist & N/A & 37min 51s \\ \hline
    Generate the package & N/A & 13min 37s \\ \hline
    Actual Analysis & 31min 44s & 13min 1s \\ \hline
    Total & 61min 20s & N/A \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

>>>>

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 1.16TB & 448.3MB & 6.3MB\\ \hline
        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        CVMFS & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & optFS & 862GB & N/A & 53KB \\ \hline
        AFS & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 181.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

\begin{figure}
\centering
\epsfig{file=package-info.eps, height=1.2in, width=2.5in}
\caption{Package Description Infomation}
\label{fig:package-info}
\end{figure}
The command used to generate the package containing all the files of L1 is as follows. 
`package1-4.sh` is a bash script which iterates each line of L1 and
determines the behavior according to the file type (common files, directories,
linked files) and the system call type.
The package description information is shown in Figure~\ref{fig:package-info}.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|}
    \hline
    Path used in Program & Actual Location \\ \hline
    / & /tmp/package-hep \\ \hline
    /tmp/package-hep & /tmp/package-hep \\ \hline
    /dev & /dev \\ \hline
    /misc & /misc\\ \hline
    /net & /net\\ \hline
    /proc & /proc\\ \hline
    /sys & /sys\\ \hline
    /var & /var\\ \hline
    /selinux & /selinux\\ \hline
    \end{tabular}
    \caption{Structure of Map File}
    \label{table:map-file}
\end{table}

@@

\begin{table*}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
        Solution 1& grid & CMSSW Git HTTP & email \\ \hline
        Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        Solution 4& package & package & shell script + packaging utility \\ \hline
    \end{tabular}
    \caption{The relationship of different solutions}
    \label{table:relationship}
\end{table*}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Sub-Task & Time & Percentage \\ \hline
    Software acquisition from CMSSW & 7min 24s & 21.44\% \\ \hline
    Software acquisition from Git & 9s & 0.43\% \\ \hline
    Software acquisition from Wget & 38s & 1.83\% \\ \hline
    Environment Build - SCRAM & 5min 48s & 16.80\% \\ \hline
    Environment Build - Python & 1s & 0.05\% \\ \hline
    Data analysis & 20min 31s & 59.44\% \\ \hline
    Total & 34min 31s & 100.00\% \\ \hline
    \end{tabular}
    \caption{Breakdown of Execution Time of Solution 2}
    \label{table:time-2nd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Data Category & Data Size \\ \hline
    Software from CMSSW & 448.3MB \\ \hline
    Software from Git & 73.7MB \\ \hline
    Software from Wget & 52MB \\ \hline
    HDFS & 43.3GB \\ \hline
    Total & 43.86GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 2}
    \label{table:datasize-2nd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|}
    \hline
    Sub-Task & Time \\ \hline
    Obtain file namelist & 28min 23s \\ \hline
    Generate P1 & 85min 51s \\ \hline
    Re-run the program within P1 & 13min 4s \\ \hline
    \end{tabular}
    \caption{Time Breakdown of Solution 4}
    \label{table:time-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|l|r|}
    \hline
    Data Category &Location & Data Size \\ \hline
    HDFS & hadoop &20GB \\ \hline
    PanFS & opt & 1.6MB \\ \hline
    CVMFS & cvmfs &103MB \\ \hline 
    NDCMS & opt &53KB \\ \hline
    AFS & afs &34MB \\ \hline
    Local FS& bin etc lib lib64 sbin tmp usr&68.3MB \\ \hline
    Total & &21GB \\ \hline
    \end{tabular}
    \caption{Data Size of Solution 4}
    \label{table:datasize-3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
     Data Category & Data Size & Data Size \\
    & Solution 2 & Solution 4\\ \hline
    HDFS & 43.3GB & 20GB \\ \hline
    PanFS & 155TB & 1.6MB \\ \hline
    CVMFS & 7.4GB &103MB \\ \hline
    NDCMS & 862GB &53KB \\ \hline
    AFS & 10.2GB &34MB \\ \hline
    Local FS& 110GB&68.3MB \\ \hline
    Total & 156TB &21GB \\ \hline
    \end{tabular}
    \caption{Data Size Comparison beweeen Solution 2 and 4}
    \label{table:datasize-2nd3rd}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Task Category & Execution Time & Execution Time \\
    & Solution 2 & Solution 4\\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Building & 5min 49s  & 3s \\ \hline
    Obtain file namelist & N/A & 28min 23s \\ \hline
    Generate the package & N/A & 85min 51s \\ \hline
    Actual Analysis & 20min 31s & 13min 4s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}
